Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2021-10-27 Presentations/ThirdYearPaperpres.tex

\begin{frame}{Event Studies}

@@

>>>>

\begin{frame}{Event Study}
\begin{equation*}
    y_{it}=\alpha_i+\delta_t+q_{it}'\lambda+\sum_{k=-5}^5 \beta_kz_{i,t-k} + \varepsilon_{it}
\end{equation*}

@@

\begin{frame}{Dep. Variable: Appears in Office-Based Data}
\begin{figure}[ht]
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_fullsample_office.pdf}
            \caption{\small All Physicians}
        \end{minipage}
        \hspace{0.2cm}
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_oldsample_office.pdf}
            \caption{\small Phys.$>$35yrs Experience}
        \end{minipage}
    \end{figure}
\end{frame}

\begin{frame}{Dep. Variable: Appears in Office-Based Data}
\begin{figure}[ht]
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_hosp_fullsample_office.pdf}
            \caption{\small All Physicians \\(Only 1 Hospital)}
        \end{minipage}
        \hspace{0.2cm}
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_hosp_oldsample_office.pdf}
            \caption{\small Phys.$>$35yrs Experience\\ (Only 1 Hospital)}
        \end{minipage}
    \end{figure}
\end{frame}
